Education Serves as a Deterrent to Criminal Behaviour

### 2024-03-29 paper/paper.qmd
Update figure 3

library(tidyverse)
library(palmerpenguins)
library(haven)
library(ggplot2)
library(dplyr)
library(sf)
library(gridExtra)
```

@@

@@

>>>>

library(tidyverse)
library(palmerpenguins)
library(haven)
library(ggplot2)
library(dplyr)
library(sf)
library(gridExtra)
library(patchwork)

@@

figure3_data <- read_csv(here::here("data/raw_data/reproduction_data/figure3_data.csv"))

@@

```{r}
#| echo: false
#| label: fig-rates
#| warning: false
#| fig-cap: Prior and post reform crime rates for ages 15-24

# Calculate arrest rates
figure3_data$arrest_rate_base <- exp(figure3_data$base_age)
figure3_data$arrest_rate_new <- exp(figure3_data$base_age + figure3_data$b_age)

# Plotting
# Total
total_fig <- ggplot(figure3_data[figure3_data$crime == 4, ], aes(x = age)) +
  geom_line(aes(y = arrest_rate_base, color = "prior"), stat = "identity", alpha = 1) +
  geom_line(aes(y = arrest_rate_new, color = "post",), stat = "identity", alpha = 1) +
  labs(x = "Age", y = "Estimated Arrest Rates", title = "Total") +
  scale_x_continuous(breaks = seq(15, 24, by = 1)) +
  scale_y_continuous(limits = c(0.04, 0.12), breaks = seq(0.04, 0.12, by = 0.02)) +
  scale_color_manual(name = NULL,
                    values = c("prior" = "aquamarine2", "post" = "chartreuse4"), 
                    labels = c("post", "prior")) + 
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(size = 11, hjust = 0.5),
        axis.text.x = element_text(angle = 45, size = 6.5),
        axis.text.y = element_text(angle = 45, size = 7),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.grid.major = element_blank())

# Violent
violent_fig <- ggplot(figure3_data[figure3_data$crime == 1, ], aes(x = age)) +
  geom_line(aes(y = arrest_rate_base, color = "prior"), stat = "identity", alpha = 1) +
  geom_line(aes(y = arrest_rate_new, color = "post",), stat = "identity", alpha = 1) +
  labs(x = "Age", y = "Estimated Arrest Rates", title = "Violent") +
  scale_x_continuous(breaks = seq(15, 24, by = 1)) +
  scale_y_continuous(limits = c(0, 0.032), breaks = seq(0, 0.032, by = 0.008)) +
  scale_color_manual(name = NULL,
                     values = c("prior" = "hotpink", "post" = "darkred"), 
                     labels = c("post", "prior")) + 
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(size = 11, hjust = 0.5),
        axis.text.x = element_text(angle = 45, size = 6.5),
        axis.text.y = element_text(angle = 45, size = 7),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.grid.major = element_blank())

# Property
property_fig <- ggplot(figure3_data[figure3_data$crime == 2, ], aes(x = age)) +
  geom_line(aes(y = arrest_rate_base, color = "prior"), stat = "identity", alpha = 1) +
  geom_line(aes(y = arrest_rate_new, color = "post",), stat = "identity", alpha = 1) +
  labs(x = "Age", y = "Estimated Arrest Rates", title = "Property") +
  scale_x_continuous(breaks = seq(15, 24, by = 1)) +
  scale_y_continuous(limits = c(0, 0.06), breaks = seq(0, 0.06, by = 0.015)) +
  scale_color_manual(name = NULL,
                     values = c("prior" = "deepskyblue", "post" = "blue"), 
                     labels = c("post", "prior")) + 
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(size = 11, hjust = 0.5),
        axis.text.x = element_text(angle = 45, size = 6.5),
        axis.text.y = element_text(angle = 45, size = 7),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.grid.major = element_blank())

# Drugs
drugs_fig <- ggplot(figure3_data[figure3_data$crime == 3, ], aes(x = age)) +
  geom_line(aes(y = arrest_rate_base, color = "prior"), stat = "identity", alpha = 1) +
  geom_line(aes(y = arrest_rate_new, color = "post",), stat = "identity", alpha = 1) +
  labs(x = "Age", y = "Estimated Arrest Rates", title = "Drugs") +
  scale_x_continuous(breaks = seq(15, 24, by = 1)) +
  scale_y_continuous(limits = c(0, 0.036), breaks = seq(0, 0.036, by = 0.009)) +
  scale_color_manual(name = NULL,
                     values = c("prior" = "gray45", "post" = "black"), 
                     labels = c("post", "prior")) + 
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(size = 11, hjust = 0.5),
        axis.text.x = element_text(angle = 45, size = 6.5),
        axis.text.y = element_text(angle = 45, size = 7),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        panel.grid.major = element_blank())

# Arrange plots using patchwork
figure3 <- total_fig + violent_fig +
  plot_layout(ncol = 2) +
  property_fig + drugs_fig

# Print the combined plot
print(figure3)
```
